Automated Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-02 paper.tex
updated title
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added comment
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Verification and Synthesis of Embedded Systems: Advances and Challenges}

@@

Automated and formal verification have been employed to ensure the correctness and reliability of CPS during the last decade, as well as controller synthesis for CPS and HS. A CPS $S$ is a tuple $S=(X,X_{0},U,Y,r,v)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, $Y$ is the set of outputs, $r$ is a transition function such that $r:X\times U \rightarrow X$, and  $v$ is an output mapping function such that $v:X\times U \rightarrow Y$~\cite{Rungger16,Alur00,Girard11}.

The overall process of formal and automated synthesis for CPS and HS involves three main steps: modeling, that is related to obtain a sound mathematical representation that is able to capture all the relevant aspects of continuous and discrete dynamics and their interaction, as well as formulate properties and invariants that describe the desirable behavior; verification, where the CPS behavior is checked through the proposed mathematical structure and the attendance of the desired behavior is verified; and, finally, the controller synthesis itself, that produces a controller or finds invariant control laws that are able to make the CPS, modeled according to the first step (modeling), meets the requirements and behaves as desired, as confirmed by the verification step.

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges}

@@

Automated and formal verification have been employed to ensure the correctness and reliability of CPS during the last decade, as well as controller synthesis for CPS and HS \textcolor{red}{add citations}. A CPS $S$ is a tuple $S=(X,X_{0},U,Y,r,v)$, where $X$ is a set of reachable states, $X_{0}$ is a set of initial states, $U$ is a set of inputs, $Y$ is the set of outputs, $r$ is a transition function such that $r:X\times U \rightarrow X$, and  $v$ is an output mapping function such that $v:X\times U \rightarrow Y$~\cite{Rungger16,Alur00,Girard11}.

The overall formal and automated synthesis process for CPS and HS involves three main steps: \textit{modeling}, which is related to obtain a sound mathematical representation able to capture all relevant aspects of continuous and discrete dynamics and their interaction, as well as, formulate properties and invariants that describe the desirable behavior; \textit{verification}, where the CPS behavior is checked through the proposed mathematical structure and the attendance of the desired behavior is verified; and, finally, the controller \textit{synthesis} itself, that produces a controller or finds invariant control laws that allow the CPS, modeled according to the first step (\textit{modeling}), to meet the requirements and behave as desired, as confirmed by the verification step.
